Towards a standardized evaluation of multiple imputation routines

### 2022-02-03 Manuscript/StandardizedEvaluation.Rmd
Add kable table

```{r sim_nobs, echo=FALSE, cache=TRUE, paged.print=TRUE}
# setup
set.seed(1)
n_sim <- 2

@@

gtsummary::tbl_summary(sim_nobs, by = method)
sim_mech %>% 
  group_by(mis_mech, corr) %>% 
  summarise(
    mean_cca = mean(mean_cca - 10),
    mean_est = mean(mean_est - 10),
    beta_cca = mean(beta_cca - corr),
    beta_est = mean(beta_est - corr),
    beta_ciw = mean(beta_ciw),
    beta_cr = mean(beta_cr),
    rmse_pred = mean(rmse_pred),
    rmse_cell = mean(rmse_cell))
```

@@

```{r sim_mech_corr, echo=FALSE, cache=TRUE, paged.print=TRUE}
# setup
set.seed(1)
n_sim <- 10
correlations <- c(0, .4, .8)
mechanisms <- c("MCAR", "MAR", "MNAR")

sim_mech <- purrr::map_dfr(1:n_sim, function(.i){
   purrr::map_dfr(correlations, function(.c){
     purrr::map_dfr(mechanisms, function(.m){
       run(corr = .c, mis_mech = .m) %>% cbind(sim = .i, .)})})})
sim_mech %>% 
  group_by(mis_mech, corr) %>% 
  summarise(
    mean_cca = mean(mean_cca - 10),
    mean_est = mean(mean_est - 10),
    beta_cca = mean(beta_cca - corr),
    beta_est = mean(beta_est - corr),
    beta_ciw = mean(beta_ciw),
    beta_cr = mean(beta_cr),
    rmse_pred = mean(rmse_pred),
    rmse_cell = mean(rmse_cell))
```

>>>>

```{r sim_nobs, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, paged.print=TRUE}
# setup
set.seed(1)
n_sim <- 100

@@

# gtsummary::tbl_summary(sim_nobs, by = dat)
# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html#Group_rows_via_labeling
sim_nobs %>% 
  group_by(n_obs, dat) %>% 
  summarise(
    mean_Y = mean(ave),
    beta_X = mean(est),
    CIW = mean(ciw),
    CR = mean(cov),
    RMSE_pred = mean(rmse_pred),
    RMSE_cell = mean(rmse_cell, na.rm = TRUE))  %>% 
  .[, -1] %>% 
  knitr::kable(
    col.names = c("", "$\\mu_{Y} = 10$", "$\\beta_{X} = 0.4$", "CIW", "CR", "RMSE$_{p}$", "RMSE$_{c}$"), 
    digits = 3,
    escape = FALSE) %>% 
  kableExtra::kable_classic(full_width = TRUE) %>% 
  kableExtra::pack_rows(group_label = "$n = 50$", 1, 3) %>% 
  kableExtra::pack_rows(group_label = "$n = 500$", 4, 6) %>% 
  kableExtra::pack_rows(group_label = "$n = 5000$", 7, 9)

@@

```{r sim_mech_corr, echo=FALSE, cache=TRUE, paged.print=TRUE}
# # setup
# set.seed(1)
# n_sim <- 10
# correlations <- c(0, .4, .8)
# mechanisms <- c("MCAR", "MAR", "MNAR") 
# 
# sim_mech <- purrr::map_dfr(1:n_sim, function(.i){
#    purrr::map_dfr(correlations, function(.c){
#      purrr::map_dfr(mechanisms, function(.m){
#        run(corr = .c, mis_mech = .m) %>% cbind(sim = .i, .)})})})
# sim_mech %>% 
#   group_by(mis_mech, corr) %>% 
#   summarise(
#     mean_cca = mean(mean_cca - 10),
#     mean_est = mean(mean_est - 10),
#     beta_cca = mean(beta_cca - corr),
#     beta_est = mean(beta_est - corr),
#     beta_ciw = mean(beta_ciw),
#     beta_cr = mean(beta_cr),
#     rmse_pred = mean(rmse_pred),
#     rmse_cell = mean(rmse_cell))
```
